|

### 2022-07-25 manuscript.Rmd
add sonify example

<!-- ```{r manual-alt, fig.cap = "Figure caption.", fig.alt = "Alt text."} -->
# knitr::include_graphics("path/to/file.png")
<!-- ``` -->

@@

Our definition of sonification refers to a data representation method using stereo sound and various audible patterns. For example, `plot(x = 1:5, y = 1:5)` can be sonified using `sonify::sonify(x = 1:5, y = 1:5)` [@R-sonify]. 
In this example, a scatter plot is represented by a sound. Position on the X axis is communicated using the left-to-right stereo effect; the pitch of the sound indicates position on the Y axis.

@@

>>>>

<!-- @mine -- Please add example figure with with manual alt text. -->

@@

Our definition of sonification refers to a data representation method using stereo sound and various audible patterns. For example, Figure \ref{fig:plot-xy} can be made audible by using `sonify` package [@R-sonify] via `r sonify::sonify(x = 1:5, y = 1:5)`.
In this example, a scatter plot is represented by a sound. Position on the X axis is communicated using the left-to-right stereo effect; the pitch of the sound indicates position on the Y axis.

@@

```{r plot-xy, fig.cap="Visualizing the relationship of two numerical variables with scatter plot.", fig.alt="Scatter plot representing the positive relationship between x and y variables.", echo=FALSE}
# Prepare variables
x <- 1:5
y <- 1:5

# Representing the relationship between x and y variables via plot visualization
plot(x, y)
```

<!-- ```{r sonify-x-y, echo=TRUE, include=TRUE}
# Representing the relationship between the two numerical variables via stereo sound
library(sonify())
sonify(x, y)
``` -->
